Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-24 Grassmannian_cells.tex
Lemma 3.15

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
  %We proceed by induction on $m$.
  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

>>>>

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}We use some of the ideas of the proof of \cite[Lemma IV.1.7]{ass}. For every proper subrepresentation $X$ of $P_{m+1}^V$ together with the natural embedding $\iota$, we get a pullback diagram
\[\xymatrix{0 \ar[r] & P_m\otimes V \ar@{=}[d]\ar^f[r] & E\ar^g[r]\ar^h[d] & X \ar^{\iota}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes V \ar^{ev_V}[r] & P_{m+1} \ar^{\pi_{m+1}^V}[r] & P_{m+1}^V \ar[r] & 0}\]

  Since the map $ev_V$ is irreducible, $f$ is either a section or $h$ a retraction.  As $h$ is injective by the Snake lemma, it cannot be a retraction. It follows that $f$ is a section and thus $g$ a retraction. Thus we find a morphism $g':X\to E$ such that $g\circ g'=\mathrm{id}_X$. We obtain
	$$\iota=\iota\circ\mathrm{id}_X=\iota\circ g\circ g'=\pi_{m+1}^V \circ h\circ g',$$i.e. $\iota$ factors through $P_{m+1}$,	and the claim follows from Lemma~\ref{le:preprojective subs}.
  %We proceed by induction on $m$.
  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
